Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-20 ms.tex
reminder

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc
(their Fig.~6) which looks qualitatively similar to the shape density
profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid
line).  To obtain such a flattening on the inferred radial scales
would require a black hole of $\Mbh\sim 10^7 \Msun$.  However, this is
inconsistent with the break in the gas density seen at $\sim 0.6$ pc
by \citet{BergerZauderer+:2012a}, which should correspond to the break
radius of the {\it stellar density} profile, thus implying an
unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.

>>>>

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc
(their Fig.~6) which looks qualitatively similar to the shape density
profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid
line).  To obtain such a flattening on the inferred radial scales
would require a black hole of $\Mbh\sim 10^7 \Msun$.  However, this is
inconsistent with the break in the gas density seen at $\sim 0.6$ pc
by \citet{BergerZauderer+:2012a}, which should correspond to the break
radius of the {\it stellar density} profile, thus implying an
unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
the mean $r_b-M_{\bullet}$ relationship
\citep{LauerFaber+:2007a}. {\bf Other constraints on gas density:
  J1644 gone mad}
